EvoSuite at the SBST 2017 Tool Competition

### 2017-02-17 papers/sbst17/paper_sbst17.tex
SBST17 draft

%\documentclass[10pt, conference, compsocconf]{IEEEtran}
%\documentclass[10pt,conference,compsocconf]{IEEEtran}
\documentclass{sig-alternate}

@@

\CopyrightYear{2016} 
\setcopyright{rightsretained} 
\conferenceinfo{ICSE '16}{May 16-17 2016, Austin, TX, USA} 
\isbn{978-1-4503-4166-0/16/05}
\doi{http://dx.doi.org/10.1145/2897010.2897020}

@@

%\title{Unit Testing Tool competition: Results for EvoSuite}
\title{EvoSuite at the SBST 2016 Tool Competition}

\numberofauthors{2}
\author{
\alignauthor
Gordon Fraser\\
       \affaddr{University of Sheffield}\\
%       \affaddr{Dep. of Computer Science}\\
       \affaddr{Sheffield, UK}
\alignauthor
 Andrea Arcuri \\
       \affaddr{Scienta, Norway}\\
       \affaddr{and University of Luxembourg}\\
%      \affaddr{P.O. Box 134, 1325 Lysaker, Norway}\\
%       \email{arcuri@simula.no}
}

@@

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
<concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011074.10011784</concept_id>
<concept_desc>Software and its engineering~Search-based software engineering</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011073</concept_id>
<concept_desc>Software and its engineering~Software maintenance tools</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Software testing and debugging}
\ccsdesc[500]{Software and its engineering~Search-based software engineering}

%
%  Use this command to print the description
%
\printccsdesc

\keywords{test case generation; search-based testing; testing classes;
  search-based software engineering}

@@

\begin{table*}[t]
  \centering
  \caption{\label{table:coverage_results}Detailed coverage results of \EVOSUITE on the SBST benchmark classes.}
\resizebox{0.8\textwidth}{!}{  
\input{coverageTable.tex}
}
\end{table*}

\begin{table*}[t]
  \centering
  \caption{\label{table:fault_results}Detailed fault detection results of \EVOSUITE on the SBST benchmark classes.}
\resizebox{0.8\textwidth}{!}{  
\input{faultTable.tex}
}	
\end{table*}

@@

>>>>

%\documentclass[10pt, conference, compsocconf]{IEEEtran}
%\documentclass[10pt,conference,compsocconf]{IEEEtran}
\documentclass[10pt,conference]{IEEEtran}

@@

@@

%\title{Unit Testing Tool competition: Results for EvoSuite}
\title{EvoSuite at the SBST 2017 Tool Competition}

\author{\IEEEauthorblockN{Authors}}

@@

@@

\begin{table*}[t]
  \centering
  \caption{\label{table:coverage_results}Detailed coverage results of \EVOSUITE on the SBST benchmark classes.}
\resizebox{0.8\textwidth}{!}{  
%\input{coverageTable.tex}
}
\end{table*}

\begin{table*}[t]
  \centering
  \caption{\label{table:fault_results}Detailed fault detection results of \EVOSUITE on the SBST benchmark classes.}
\resizebox{0.8\textwidth}{!}{  
%\input{faultTable.tex}
}	
\end{table*}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
